% CV: Bradley Worley.
\documentclass[letterpaper]{article}
%===============================================================================

% Include required packages.
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Name (title) field.
\def\name{Bradley Worley}

% Set to \def\footerlink{} to remove this link from the footer
\def\footerlink{http://geekysuavo.github.io/}

% The following metadata will show up in the PDF properties.
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {chemistry, physics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

% Set up page margins.
\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=0.50in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

% Make enumerated list numbers bolded.
\renewcommand{\labelenumi}{
  \bf{\arabic{enumi}.}
}

% Start the document.
\begin{document}

% Place name at left
{\huge \name}
\vspace{0.25in}

%===============================================================================
\begin{minipage}{0.45\linewidth}
  Unit\'{e} de Bioinformatique Structurale \\
  \href{http://www.pasteur.fr/}{Institut Pasteur -- Paris} \\
  25 rue du Dr. Roux \\
  Paris, France 75015
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Cell: &  +33 07 68 72 87 70 \\
    Email: & \href{mailto:geekysuavo@gmail.com}
                     {\tt geekysuavo@gmail.com} \\
    Homepage: & \href{http://geekysuavo.github.io/}
                 {\tt http://geekysuavo.github.io/} \\
  \end{tabular}
\end{minipage}


%===============================================================================
\section*{Education}

\begin{itemize}
  \item Ph.D. Chemistry, University of Nebraska--Lincoln, 2015.
  \begin{itemize}
    \item \emph{Dissertation:} ``Chemometric and Bioinformatic Analyses
      of Cellular Biochemistry''
    \item \emph{Committee:}
      R. Powers, E.~D. Dodds, D.~S. Hage,
      G.~S. Harbison, S.~D. Scott
  \end{itemize}
  \item Summa Cum Laude, B.S. Biochemistry, Texas Tech University, 2010.
\end{itemize}


%===============================================================================
\section*{Interests}

\begin{itemize}
\item{
  Developing statistically robust biophysical techniques and tools to better
  understand cellular biochemistry and protein folding.
}
\item{
  Mastering techniques of software architecture and electronics design.
}
\item{
  Swimming, cycling, and folk songwriting.
}
\end{itemize}


%===============================================================================
\section*{Software Experience}

\begin{itemize}
\item{
  Expert in implementation of multivariate statistical algorithms,
  especially latent-variable and Bayesian models.
}
\item{
  Experience in projects spanning from systems-level architecture to
  register-level firmware.
}
\item{
  Expert in C, Regular Expressions and GNU/Linux shell scripting and
  system administration.
}
\item{
  Highly proficient in Python, Perl, PHP, Javascript and HTML/CSS.
}
\end{itemize}


%===============================================================================
\section*{Research Experience}

\begin{itemize}
\setlength{\itemsep}{16pt}
\item{
  {\it Pasteur Foundation Postdoctoral Fellow}
  \hfill 2016--2019. \\
  Structural Bioinformatics Unit, Pasteur Institute \\
  Head of Unit: Dr. Michael Nilges \\
  \begin{enumerate*}
    \item Enhancement of the {\it interval} Branch-and-Prune
    ({\it i}BP) algorithm for exhaustive solution enumeration in the
    Molecular Distance Geometry problem.
    \item Advancement of machine learning methods in bioinformatics,
    chemometrics and structural biology.
  \end{enumerate*}
}

\pagebreak
\item{
  {\it NMR Facility Teaching Assistant}
  \hfill 2012--2015. \\
  Department of Chemistry, University of Nebraska-Lincoln \\
  Advisor: Dr. Martha Morton
  \begin{enumerate*}
    \item Maintenance of five Nuclear Magnetic Resonance (NMR) spectrometers,
      including $N_2$ and $He$ fills, software and hardware troubleshooting.
    \item Training of researchers new to NMR spectroscopy.
  \end{enumerate*}
}

\item{
  {\it Graduate Research Assistant}
  \hfill 2010--2015. \\
  Department of Chemistry, University of Nebraska-Lincoln \\
  Advisor: Dr. Robert Powers
  \begin{enumerate*}
    \item Development of an end-to-end software suite for chemometric data
      handling in $^1$H NMR metabolic fingerprinting studies (MVAPACK).
    \item Development of a comprehensive database solution for the Functional
      Annotation Screening Technology by NMR (FAST-NMR).
    \item Analysis of Pancreatic cancer-associated proteomics and genomics
      datasets for the identification of novel drug targets.
    \item System administration of all Windows and Linux computing resources
      in the group.
  \end{enumerate*}
}

\item{
  {\it Undergraduate Research Assistant}
  \hfill 2007--2009. \\
  Department of Chemistry and Biochemistry, Texas Tech University \\
  {\setlength{\topmargin}{0pt} Advisor: Dr. Edward Quitevis}
  \begin{enumerate*}
    \item Rotational dynamics of room-temperature ionic liquids at and near
      the glass-transition temperature by Fluorescence Recovery After
      Photobleaching (FRAP).
  \end{enumerate*}
}
\end{itemize}


%===============================================================================
\section*{Professional Experience}

\subsection*{Research Mentorship}

\begin{itemize}
\item{
  {\it Undergraduate Research Mentor}
  \hfill 2011--2013. \\
  Department of Chemistry, University of Nebraska-Lincoln
  \begin{enumerate*}
    \item Responsible for supervising an undergraduate student in NMR
      protein-ligand binding studies using FAST-NMR.
  \end{enumerate*}
}
\end{itemize}

\subsection*{Scientific Outreach}

\begin{itemize}
 \item Pasteur Institute Postdoctoral Representative \hfill 2016--2019.
 \item Phi Labmda Upsilon, Rho Chapter Secretary \hfill 2012.
 \item UNL Chemistry Day Volunteer \hfill 2010--2015.
\end{itemize}

\subsection*{Awards and Scholarships}

\begin{itemize}
 \item ENC {\it Journal of Magnetic Resonance}
  Young Scientist Award \hfill 2018.
 \item Pasteur Foundation Postdoctoral Fellow \hfill 2016--2019.
 \item Department of Education GAANN Fellow \hfill 2010--2012.
\end{itemize}


%===============================================================================
\section*{Publications}

\subsection*{Journal Articles}

%\item J. L. Stark, \textbf{B. Worley} and R. Powers,
% Using Chemical Shift Perturbations to Guide and Filter Docking Results
% with CSP-Consensus and AutoDockFilter 2,
% {\it BMC Research Notes},
% In preparation.

%\item \textbf{B. Worley}, T. E. Malliavin and M. Nilges,
% Fast Bayesian time-domain NMR mixture analysis,
% {\it Journal of Magnetic Resonance},
% In preparation.

%\item \textbf{B. Worley}, T. E. Malliavin and M. Nilges,
% Active nonuniform sampling,
% {\it Journal of Magnetic Resonance},
% In preparation.

\begin{itemize}
 \item \textbf{B. Worley}
  Expectation Propagation for sparse Bayesian Learning,
  \emph{Journal of Machine Learning Research},
  In preparation.

 \item \textbf{B. Worley}, T. E. Malliavin and M. Nilges,
  Scalable Variational Relevance Vector Machines,
  \emph{Journal of Machine Learning Research},
  In preparation.

 \item \textbf{B. Worley}, T. E. Malliavin, M. Nilges,
  Variational Features for Regression and Classification,
  \emph{JMLR Machine Learning Open Source Software},
  In preparation.

 \item \textbf{B. Worley},
  Variational Bayesian Analysis of NUS NMR Data,
  \emph{Concepts in Magnetic Resonance},
  In press.

 \item \textbf{B. Worley}, T. E. Malliavin, B. Bardiaux, N. Wolff,
  M. Nilges, C. Lavor and L. Liberti, Tuning interval Branch-and-Prune
  for protein structure determination,
  \emph{Journal of Global Optimization},
  2018, 72: 109--127.

 \item C. Lavor, L. Liberti, B. Donald, \textbf{B. Worley},
  B. Bardiaux, T. E. Malliavin and M. Nilges, Minimal NMR distance
  information for rigidity of protein graphs,
  \emph{Discrete Applied Mathematics},
  In press.

 \item R. Powers, S. Lei, D. D. Marshall, \textbf{B. Worley}, A. Anandhan,
  R. L. Cerny, E. D. Dodds, Y. Huang, M. I. Panayiotidis, A. Pappa,
  R. Franco, Metabolic Investigations of Molecular Mechanisms
  Associated with Parkinson's Disease,
  \emph{Metabolites},
  2017, 7(2): 22.

 \item J. Catazaro, J. Periago, M. D. Shortridge, \textbf{B. Worley},
  A. Kirchner, R. Powers and M. A. Griep,
  Identification of a ligand binding site on the
  \emph{Staphylococcus aureus} DnaG primase C-terminal domain,
  \emph{Biochemistry}, 2017, 56(7): 932--943.

 \item \textbf{B. Worley} and R. Powers,
  PCA as a Predictor of OPLS-DA Model Reliability,
  \emph{Current Metabolomics},
  2016, 4: 97--103.

 \item \textbf{B. Worley},
  Subrandom Methods for Multidimensional Nonuniform Sampling,
  \emph{Journal of Magnetic Resonance},
  2016, 269: 128--137.

 \item \textbf{B. Worley},
  Convex Accelerated Maximum Entropy Reconstruction,
  \emph{Journal of Magnetic Resonance},
  2016, 265: 90--98.

 \item P. Quint, S. Scott, V. Vinodchandran and \textbf{B. Worley},
  Constrained Group Testing to Predict Binding
  Response of Candidate Compounds,
  \emph{SIAM International Conference on Data Mining}, 2016.

 \item \textbf{B. Worley} and R. Powers,
  A Sequential Algorithm for Multiblock Orthogonal Projections
  to Latent Structures,
  \emph{Chemometrics and Intelligent Laboratory Systems},
  2015, 149: 33--39.

 \item \textbf{B. Worley} and R. Powers,
  Deterministic Multidimensional Nonuniform Gap Sampling,
  \emph{Journal of Magnetic Resonance},
  2015, 261: 19--26.

 \item \textbf{B. Worley}, N. J. Sisco and R. Powers,
  Statistical Removal of Background Signals from High-throughput $^1$H NMR
  Line-broadening Ligand-affinity Screens,
  \emph{Journal of Biomolecular NMR},
  2015, 63(1): 53--58.

 \item \textbf{B. Worley} and R. Powers,
  Generalized Adaptive Intelligent Binning of Multiway Data,
  \emph{Chemometrics and Intelligent Laboratory Systems},
  2015, 146: 42--46.

 \item \textbf{B. Worley}$^\dagger$, D. D. Marshall$^\dagger$,
  S. Lei$^\dagger$, Y. Huang, A. Garcia-Garcia, R. Franco,
  E. D. Dodds and R. Powers, Combining DI-ESI-MS and NMR Datasets for
  Metabolic Profiling,
  \emph{Metabolomics},
  2015, 11: 391--402.

 \item \textbf{B. Worley} and R. Powers,
  MVAPACK: A Complete Data Handling Package for NMR Metabolomics,
  \emph{ACS Chemical Biology},
  2014, 9(5): 1138--1144.

 \item \textbf{B. Worley} and R. Powers,
  Simultaneous Phase and Scatter Correction for NMR Datasets,
  \emph{Chemometrics and Intelligent Laboratory Systems},
  2013, 131(2014): 1--6.

 \item \textbf{B. Worley} and R. Powers,
  Multivariate Analysis in Metabolomics,
  \emph{Current Metabolomics},
  2013, 1(1): 92--107.

 \item \textbf{B. Worley}, S. Halouska and R. Powers,
  Utilities for Quantifying Separation in PCA/PLS-DA Scores Plots,
  \emph{Analytical Biochemistry},
  2012, 433(2): 102--104.

 \item \textbf{B. Worley}, G. Richard, G. S. Harbison and R. Powers,
  $^{13}$C NMR Reveals no Evidence of $n\rightarrow\pi^*$ Interactions
  in Proteins, \emph{PLoS ONE},
  2012, 7(8): 166--171.
\end{itemize}

\subsection*{Research Presentations}

\begin{itemize}
 \item Back to Bayes'ics: NUS Reconstruction as Statistical Inference
  \hfill ENC, 2018.

 \item Nonuniform sampling without schedules using Bayesian Active Learning
  \hfill Keystone, 2017.

 \item Viewing NMR Acquisition through a Bayesian Lens
  \hfill Pasteur RMN 2017.

 \item Accelerated MaxEnt for NUS NMR
  \hfill Pasteur-BNMRZ, 2016.

 \item Deterministic Multidimensional Nonuniform Gap Sampling
  \hfill GRASP NMR, 2015.

 \item MVAPACK: The definitive toolbox for NMR chemometrics
  \hfill ICMRBS, 2014.

 \item Simultaneous Phase and Scatter Correction of NMR Datasets
  \hfill ENC, 2013.

 \item Carbonyl $^{13}$C Chemical Shifts, $n\rightarrow\pi^*$ interactions,
  and Proteins \hfill GRASP NMR, 2010.
\end{itemize}

%===============================================================================
\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

% End the document.
\end{document}

